Toward theories of deliberated preferences

### 2020-10-26 simple.tex
Weaken claim

The descriptive theories proposed in decision theory, in the sense defined here, are exclusively shallow descriptive theories, to the best of my knowledge.
%This need not be so. Indeed, this article introduces descriptive theories about reflective behavior.
This observation permits to understand what could be called the “normative versus descriptive gap”, referring to the belief, implicit in the decision theoretic literature, that a theory cannot be both normative and descriptive. Because normative theories aim to prescribe, they are required to not yield recommendations that precisely, systematically match shallow behavior. Given the numerous results in experimental psychology showing that shallow behavior is undefensible in many situations, a normative theory whose prescriptions would systematically match shallow behavior would be suspicious, to say the least. It would also be of low practical interest.
It is an immediate consequence of this minimal requirement that a normative theory cannot also be a shallow descriptive theory. 
In other words, as \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow behavior is not sufficient to inform normative economics.
The “normative versus descriptive gap” comes from an implicit identification of descriptive theories with shallow descriptive theories.

>>>>

The descriptive theories proposed in decision theory, in the sense defined here, are mostly shallow descriptive theories, to the best of my knowledge (\cref{sec:purification} discusses the particular case of “preference purification” approaches).
%This need not be so. Indeed, this article introduces descriptive theories about reflective behavior.
This observation permits to understand what could be called the “normative versus descriptive gap”, referring to the belief, implicit in the decision theoretic literature, that a theory cannot be both normative and descriptive. Because normative theories aim to prescribe, they are required to not yield recommendations that precisely, systematically match shallow behavior. Given the numerous results in experimental psychology showing that shallow behavior is undefensible in many situations, a normative theory whose prescriptions would systematically match shallow behavior would be suspicious, to say the least. It would also be of low practical interest.
It is an immediate consequence of this minimal requirement that a normative theory cannot also be a shallow descriptive theory. 
In other words, as \citet{hausman_preference_1994} illustrate with an example of a person drinking a fatal poison while erroneously thinking that it is water, shallow behavior is not sufficient to inform normative economics.
The “normative versus descriptive gap” comes from an implicit identification of descriptive theories with shallow descriptive theories.
